---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# drawCell

<!-- badges: start -->
<!-- badges: end -->

The goal of drawCell is to easily obtain nice cell pictures in R!



## Installation

drawCell needs the package [webshot2](https://github.com/rstudio/webshot2), which needs to be installed. 

To obtain the cell pictures, draCell connects to the [SwissBioPics API](https://www.swissbiopics.org/) so an internet connection is required.

``` r
# install.packages("devtools")
devtools::install_github("svalvaro/MQmetrics")
```

## Example

This is a basic example which shows you how to solve a common problem:



It requires the [taxonomy id](https://www.ncbi.nlm.nih.gov/taxonomy/) of your species of interest, and one or multiple SL codes for subcellular locations that will be colored. [This dataset ](http://current.geneontology.org/ontology/external2go/uniprotkb_sl2go) contains the SL codes for each subcellular location.


The taxonomy id for *Quercus ilex* a common tree in the south of Spain is `58334` and as an example I will use the SL code of the chloroplast: `0049`.

```{r plantcell, message=FALSE}

library(drawCell)

drawCell(taxonomy_id = '58334', sl_ids = '0049')

```
We can also obtain pictures of viruses, yeast, and pretty much everything that exists!

For the baker's yeast *Saccharomyces cerevisiae* whose taxonomy id is `4932` we will highlight the nucleus: `0191` and the vacuole: `0272`.

```{r sacc, message=F}

drawCell(taxonomy_id = '4932', sl_ids = c('0191', '0272'))
```





