---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r options1, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
  # echo = FALSE, 
  # message = FALSE,
  # warning = FALSE,
  # error = FALSE
)
```

# drawCell

<!-- badges: start -->
<!-- badges: end -->

The goal of drawCell is to easily obtain nice cell pictures in R!

## Installation

To obtain the cell pictures, `drawCell` connects to the
[SwissBioPics API](https://www.swissbiopics.org/) so an internet connection 
is required.

``` {r installation, eval= FALSE}
# install.packages("devtools")
devtools::install_github("svalvaro/drawCell")
```

## Examples

It requires the [taxonomy id](https://www.ncbi.nlm.nih.gov/taxonomy/) of your
species of interest, and one or multiple SL codes for subcellular locations 
that will be colored. The SL codes for each subcellular location can be found at
[Uniprot](https://www.uniprot.org/docs/subcell) and
[uniprotkb_sl2go](http://current.geneontology.org/ontology/external2go/uniprotkb_sl2go).

To generate a cell of Homo sapiens (Taxonomy id: `9606`) with
highlighted Endoplasmic Reticulum (SL code: `0095`) and lipid droplets 
(SL code: `0154`):

```{r animal_cell,  results='hide', message=F, warning=FALSE, error=F}

library(drawCell)

drawCell(organism_identifier = '9606', list_sl_colors = list("SL0173" = "red", "SL0101" = "blue"))
```

The `organism_identifier` for *Quercus ilex* a common tree in the south of Spain is
`58334` and as an example I will use the SL code of the chloroplast: `0049`.

```{r plantcell,  results='hide', message=F, warning=FALSE, error=F}

drawCell(organism_identifier = '58334', list_sl_colors = list("SL0049" = 'lightgreen'))
```

We can also obtain pictures of viruses, yeast, and pretty much everything that
exists!

For the baker's yeast *Saccharomyces cerevisiae* whose `organism_identifier` is `4932` 
we will highlight the nucleus: `0191` and the vacuole: `0272`.

```{r sacc2, results='hide', message=F, warning=FALSE, error=F}

drawCell(organism_identifier = '4932', list_sl_colors = list("SL0191" = "pink", "SL0272" = "yellow"))
```
