---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# drawCell

<!-- badges: start -->
<!-- badges: end -->

The goal of drawCell is to easily obtain nice cell pictures in R!

## Installation

drawCell is not available at CRAN or bioconductor since it uses the package [webshot2](https://github.com/rstudio/webshot2), which needs to be installed. 

``` r
# install.packages("devtools")
devtools::install_github("svalvaro/MQmetrics")
```

## Example

This is a basic example which shows you how to solve a common problem:



It requires the [taxonomy id](https://www.ncbi.nlm.nih.gov/taxonomy/) of your species of interest, and one or multiple SL codes for subcellular locations that will be colored. [This dataset ](http://current.geneontology.org/ontology/external2go/uniprotkb_sl2go) contains the SL codes for each subcellular location.


The taxonomy id for *Quercus ilex* a common tree in the south of Spain is `58334` and as an example I will use the SL code of the chloroplast: `0049`.

```{r example, message=FALSE,   fig.width= 9.4}

library(drawCell)

drawCell(taxonomy_id = '58334', sl_ids = '0049')

```





