---
title: "drawCell"
author: "Alvaro Sanchez-Villalba"
output: BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{drawCell}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---
  
```{r options2, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  purl = FALSE
)
```

# Overview

The package drawCell provides the functionality to generate cell pictures 
with highlighted subcellular organelles with R. 

It uses the [SwissBioPics API](https://www.swissbiopics.org/) so an internet
connection is required to use this package.

# Installation

Install dev version of `drawCell`:

```{r install2, eval = FALSE}
# install.packages("devtools")
devtools::install_github("svalvaro/drawCell")
```

# How to use

It is fairly simple to use `drawCell`. You just need to know the 
[`organism_identifier`](https://www.ncbi.nlm.nih.gov/taxonomy/) of
your species of interest, and one or multiple SL codes for subcellular
locations that will be colored. The SL codes for each subcellular
location can be found at [Uniprot](https://www.uniprot.org/docs/subcell)
and
[uniprotkb\_sl2go](http://current.geneontology.org/ontology/external2go/uniprotkb_sl2go).

# Examples

The organism_identifier for *Quercus ilex* a common tree in the south of Spain
is `58334` and as an example I will use the SL code of the chloroplast:
`0049`.

The size of the picture can be chosen with `size` and the colour_sl with `colour_sl`.

```{r example, results='hide', message=F, warning=FALSE, error=F}

library(drawCell)

drawCell(organism_identifier = '58334', list_sl_colors = list("0049" = "red"))
```

We can also obtain pictures of viruses, yeast, and pretty much everything that 
exists!

For the baker's yeast *Saccharomyces cerevisiae* whose organism_identifier is `4932` 
we will highlight the nucleus: `0191` and the vacuole: `0272`.

```{r sacc, results='hide', message=F, warning=FALSE, error=F}
drawCell(organism_identifier = "4932", list_sl_colors = list("SL0191" = "brown", "SL0272" = "pink"))
```

If one wishes to highlight the endosomes (SL:0101) of  *Homo sapiens* 
(organism_identifier: 9606):

```{r covid, results='hide', message=F, warning=FALSE, error=F}
drawCell(organism_identifier = "9606", list_sl_colors = list("SL0101" = "blue"))
```
