---
title: "drawCell"
author: "Alvaro Sanchez-Villalba"
output: BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{drawCell}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---
  
```{r options2, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    message = FALSE,
    warning = FALSE,
    purl = FALSE
)
```



# Overview

The package drawCell provides the functionality to generate cell pictures 
with highlighted subcellular organelles with R. 

It uses the [SwissBioPics API](https://www.swissbiopics.org/) so an internet
connection is required to use this package.


# How to use

It is fairly simple to use `drawCell`. You just need to know the 
[taxonomy id](https://www.ncbi.nlm.nih.gov/taxonomy/) of
your species of interest, and one or multiple SL codes for subcellular
locations that will be colored. The SL codes for each subcellular
location can be found at [Uniprot](https://www.uniprot.org/docs/subcell)
and
[uniprotkb\_sl2go](http://current.geneontology.org/ontology/external2go/uniprotkb_sl2go).



# Examples

The taxonomy id for *Quercus ilex* a common tree in the south of Spain
is `58334` and as an example I will use the SL code of the chloroplast:
`0049`.

```{r example, message=FALSE, warning=FALSE, results='hide'}
library(drawCell)
drawCell(taxonomy_id = '58334', sl_ids = '0049', delay = 3)
```


We can also obtain pictures of viruses, yeast, and pretty much everything that 
exists!

For the baker's yeast *Saccharomyces cerevisiae* whose taxonomy id is `4932` 
we will highlight the nucleus: `0191` and the vacuole: `0272`.

```{r sacc, message=F, results='hide'}
drawCell(taxonomy_id = '4932', sl_ids = c('0191', '0272'), delay = 3)
```



If one wishes to highligth the endosomes (SL:0101) of  *Homo sapiens* 
(Taxonomy id: 9606):


```{r covid, message= FALSE, results='hide'}
drawCell(taxonomy_id = '9606', sl_ids = '0101', delay = 3 )
```



# Troubleshooting. 

If after using the function `drawCell()` you obtain an empty image, this might
be because the rendering process of that image takes longer. By default, the 
delay is one second, so if you increase it it will probably solve the issue.
```{r trouble, eval = FALSE}
# If it returns an empty image, increase the delay
drawCell(taxonomy_id = '4932' , sl_ids = '0191')

drawCell(taxonomy_id = '4932' , sl_ids = '0191', delay = 10)

```

