---
title: "drawCell"
author: "Alvaro Sanchez-Villalba"
output: BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{drawCell}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---
  
```{r options2, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    
    message = FALSE,
    warning = FALSE,
    purl = FALSE
)
```



# Overview

The package drawCell provides the functionality to generate cell pictures 
with highlighted subcellular organelles with R. 

It uses the [SwissBioPics API](https://www.swissbiopics.org/) so an internet
connection is required to use this package.


# How to use

It is fairly simple to use `drawCell`. You just need to know the 
[taxonomy id](https://www.ncbi.nlm.nih.gov/taxonomy/) of
your species of interest, and one or multiple SL codes for subcellular
locations that will be colored. The SL codes for each subcellular
location can be found at [Uniprot](https://www.uniprot.org/docs/subcell)
and
[uniprotkb\_sl2go](http://current.geneontology.org/ontology/external2go/uniprotkb_sl2go).



# Examples








The taxonomy id for *Quercus ilex* a common tree in the south of Spain
is `58334` and as an example I will use the SL code of the chloroplast:
`0049`.



```{r example, message=FALSE, warning=FALSE, results='hide'}
library(drawCell)
drawCell(taxonomy_id = '58334', sl_ids = '0049', delay = 3)
```



We can also obtain pictures of viruses, yeast, and pretty much everything that exists!

For the baker's yeast *Saccharomyces cerevisiae* whose taxonomy id is `4932` we will highlight the nucleus: `0191` and the vacuole: `0272`.

```{r sacc, message=F, results='hide'}
drawCell(taxonomy_id = '4932', sl_ids = c('0191', '0272'), delay = 3)
```



If one wishes to highligth the Cytoskeleton (SL:0090) on  *Penicillium rubens* (Tax_id: 1108849):


```{r covid, message= FALSE, results='hide'}
drawCell(taxonomy_id = '1108849', sl_ids = '0090', delay = 3 )
```

